Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
corrected some superscript notation

	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w \geq 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$. It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$. Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
	\begin{equation*}
	\lim_{b_2 \to 0} \Delta SC = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
	\end{equation*}

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus,
	$$ 0 < \lim_{b_2 \to 0} SC^{MKV} < \infty.$$
	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{b_2 \to 0} > 1.$$

@@

	Now, we adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. Consider the two quantities:
	$$ I^{\bar{b}_2}_1 := \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I^{\bar{b}_2}_2: = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds. $$

@@

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	\begin{equation*}
	q_T+\bar{q}_T(1-s_T) >0,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

>>>>

	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w \geq 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$. It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$. Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
	\begin{equation*}
	\lim_{b_2 \to 0} \Delta SC^{b_2} = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
	\end{equation*}

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus,
	$$ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$$
	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA^{b_2} = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC^{b_2}}{\displaystyle \lim_{b_2 \to 0} SC^{MKV,b_2} } =: PoA^{b_2 \to 0} > 1.$$

@@

	Now, we adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0$. Consider the two quantities:
	$$ I^{\bar{b}_2}_1 := \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I^{\bar{b}_2}_2: = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds. $$

@@

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	\begin{equation*}
	q_T+\bar{q}_T(1-s_T) >0,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{b_1 \to 0} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{\bar{b}_1 \to 0} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,b_1}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$
